Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-15 paper/tex/analysis.tex
introduce implicit prior language

%\red{Maybe it would be best to introduce the summary statistics (KS, CvM, AD) up front and then the ensemble functions and stacked n(z).}

% All code runners were asked to output redshift posterior estimates on 200 linear-spaced bins between redshifts 0 and 2.

@@

Before describing the metrics appropriate to the DC1 data set, we outline the philosophy behind our choices.
A \pzpdf\ estimator derived by method $H$ must be understood as a posterior probability distribution
\begin{equation}
\hat{p}^{H}_{i}(z) \equiv p(z \vert d_{i}, I_{D}, I_{H}),
\end{equation}
conditioned not only on the photometric data $d_{i}$ for that galaxy but also on parameters encompassing a number of things that will differ depending on the method $H$ used to produce it, namely the assumptions $I_{H}$ necessary for the method to be valid and any inputs $I_{D}$ it takes as prior information, such as a template library or training set.
Because of this, direct comparison of \pzpdf s produced by different methods is in some sense impossible; even if they share the same prior information $I_{D}$, by definition they cannot be conditioned on the same assumptions $I_{H}$, otherwise they would not be distinct methods at all.

In this study, we isolate the effect of differences in prior information $I_{H}$ specific to each method by using a single training set $I_{D}^{\rm ML}$ for all machine learning-based codes and a single template library $I_{D}^{\rm T}$ for all template-based codes.
These sets of prior information are carefully constructed to be representative and complete, so we have $I_{D} \equiv I_{D}^{\rm ML} \equiv I_{D}^{\rm T}$ for every method $H$.
Thus, we are saying
\begin{equation}
\frac{\hat{p}_{i}^{H}(z)}{\hat{p}_{i}^{H'}(z)} \approx \frac{p(z \vert d_{i}, I_{H})}{p(z \vert d_{i}, I_{H'})},
\end{equation}
meaning that we assume comparisons of $\hat{p}_{i}^{H}(z)$ isolate the effect of the method used to obtain the estimator, which should enable interpetation of the differences between estimated PDFs in terms of the specifics of the method implementations.

>>>>

@@

Before describing the metrics appropriate to the DC1 data set, we outline the philosophy behind our choices.
A \pzpdf\ estimator derived by method $H$ must be understood as a posterior probability distribution
\begin{equation}
  \label{eq:pzpdf}
\hat{p}^{H}_{i}(z) \equiv p(z \vert d_{i}, I_{D}, I_{H}),
\end{equation}
conditioned not only on the photometric data $d_{i}$ for that galaxy but also on parameters encompassing a number of things that will differ depending on the method $H$ used to produce it, namely the often implicit assumptions $I_{H}$ necessary for the method to be valid and any inputs $I_{D}$ it takes as prior information, such as a template library or training set.
Because of this, direct comparison of \pzpdf s produced by different methods is in some sense impossible; even if they share the same external prior information $I_{D}$, by definition they cannot be conditioned on the same assumptions $I_{H}$, otherwise they would not be distinct methods at all.
We call $I_{H}$ the \textit{implicit prior} specific to the method, though some aspects of its nature may be discerned.

In this study, we isolate the effect of differences in prior information $I_{H}$ specific to each method by using a single training set $I_{D}^{\rm ML}$ for all machine learning-based codes and a single template library $I_{D}^{\rm T}$ for all template-based codes.
These sets of prior information are carefully constructed to be representative and complete, so we have $I_{D} \equiv I_{D}^{\rm ML} \equiv I_{D}^{\rm T}$ for every method $H$.
Under this assumption, a ratio of posteriors of codes is in effect a ratio of the implicit posteriors $p(z \vert d_{i}, I_{H'})$ since the external prior information $I_{D}$ is present in the numerator and denominator.
Thus comparisons of $\hat{p}_{i}^{H}(z)$ isolate the effect of the method used to obtain the estimator, which should enable interpretation of the differences between estimated PDFs in terms of the specifics of the method implementations.
